---
title: "TC_AC"
author: "Tyler Cobian"
date: "5/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the data and packages
```{r, include=FALSE}
library(tidyverse)
data<- read_csv("HW4Data (3).csv")

```

1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).
```{r}
# try to graph the abatement cost for the different sectors to see the form
  # added points to see the shape

# Shape of MC_a
#############################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_A))+
  geom_point() +
  geom_smooth()
mc_graph
############################################

# Shape of MC_B
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_B))+
  geom_point() +
  geom_smooth()
mc_graph
# this one only looks linear of you use geom_smooth with other ones it is pretty noisy so I am not sure if this is linear
###########################################

# Shape of MC_C
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_C))+
  geom_point() +
  geom_smooth()
mc_graph

# This one might be an exponenvtial funtion
###########################################

# Shape of MC_D
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_D))+
  geom_point() +
  geom_smooth()
mc_graph

# This one looks very noisy I cann't make out what the shape is


```

```{r}

# Regression analysis for each sector

###############################################

# Sector A looks linear so linear regression
lm_a<- lm(MC_A ~ Abatement, data = data)
summary(lm_a)
plot(lm_a) # check fit

# store parameters
int_a <- lm_a$coefficients[1]
slope_a <- lm_a$coefficients[2]

###############################################

# try linear regression for Sector b
lm_b <- lm(MC_B ~ Abatement, data = data)
summary(lm_b)
plot(lm_b)

# store parameters
int_line_b<- lm_b$coefficients[1]
slope_line_b<- lm_b$coefficients[2]


# try polynomial regression for sector b

lm_b2 <- lm(MC_B ~ Abatement + I(Abatement^2) + I(Abatement^3), data = data)
summary(lm_b2) # explains 59% of the variance vs linear model's 52% of the variance
plot(lm_b2) # residuals vs leverage don't look great but the normall QQ looks better than linear model

# store parameters
int_b <- lm_b2$coefficients[1]
slope1_b <- lm_b2$coefficients[2]
slope2_b <- lm_b2$coefficients[3]
slope3_b <- lm_b2$coefficients[4]

 # Graph it to check the fit 
b_lm_graph <- ggplot(data, aes(x=Abatement, y=MC_B)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x+I(x^2)+ I(x^3))
b_lm_graph

#############################################

# Sector C looks exponential, so exponential regression

lm_c <- lm(log(MC_C) ~ Abatement, data = data)
summary(lm_c) # explains 83% of the variance
plot(lm_c) # some of these don't look that good


# Linear model for C
lm_c<- lm(MC_C ~ Abatement, data = data)
summary(lm_c)

#store parameters
int_line_c<- lm_c$coefficients[1]
slope_line_c<- lm_c$coefficients[2]


# store the parameters
int_c <- lm_c$coefficients[1]
slope_c <- lm_c$coefficients[2]

# linear model for MC_D
lm_d<- lm(MC_D ~ Abatement, data = data)
summary(lm_d)

#Store parameters
int_line_d<- lm_d$coefficients[1]
slope_line_d<- lm_d$coefficients[2]

################################################
```
2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?
```{r}

A<- function(x){int_a + slope_a*(180-x)}
A(1)
# WTP for the first unit 94.61022 

B<- function(x){int_b + slope1_b*(200 -x) + slope2_b*(200 - x)^2 + slope3_b*(200 -x)^3}
B(1)
# WTP for the first unit 6.092104 

B_line<- function(x){int_line_b + slope_line_b*(200-x)}
B_line(1)
# WTP for the first unit is  48.86781

C<- function(x){int_c + slope_c*(220 -x)}
C(1)
# WTP for the first unit 6.666876

D_line<- function(x){int_line_d + slope_line_d*(300 - x)}
D_line(1)
# WTP for the first uit 87.40584

C_lm_graph <- ggplot(data, aes(x=Abatement, y=MC_C)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~log(x))
C_lm_graph


```















