---
title: "TC_AC"
author: "Tyler Cobian"
date: "5/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the data and packages
```{r, include=FALSE}
library(tidyverse)
data<- read_csv("HW4Data (3).csv")

```

1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).
```{r}
# try to graph the abatement cost for the different sectors to see the form
  # added points to see the shape

# Shape of MC_a
#############################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_A))+
  geom_point() +
  geom_smooth()
mc_graph
############################################

# Shape of MC_B
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_B))+
  geom_point() +
  geom_smooth()
mc_graph
# this one only looks linear of you use geom_smooth with other ones it is pretty noisy so I am not sure if this is linear
###########################################

# Shape of MC_C
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_C))+
  geom_point() +
  geom_smooth()
mc_graph

# This one might be an exponenvtial funtion
###########################################

# Shape of MC_D
###########################################
mc_graph<- ggplot(data, aes(x = Abatement, y = MC_D))+
  geom_point() +
  geom_smooth()
mc_graph

# This one looks very noisy I cann't make out what the shape is


```

```{r}

# Regression analysis for each sector

###############################################

# Sector A looks linear so linear regression
lm_a<- lm(MC_A ~ Abatement, data = data)
summary(lm_a)
plot(lm_a) # check fit

# store parameters
int_a <- lm_a$coefficients[1]
slope_a <- lm_a$coefficients[2]

###############################################

# try linear regression for Sector b
lm_b <- lm(MC_B ~ Abatement, data = data)
summary(lm_b)
plot(lm_b)

# store parameters
int_line_b<- lm_b$coefficients[1]
slope_line_b<- lm_b$coefficients[2]


# try polynomial regression for sector b

lm_b2 <- lm(MC_B ~ Abatement + I(Abatement^2) + I(Abatement^3), data = data)
summary(lm_b2) # explains 59% of the variance vs linear model's 52% of the variance
plot(lm_b2) # residuals vs leverage don't look great but the normall QQ looks better than linear model

# store parameters
int_b <- lm_b2$coefficients[1]
slope1_b <- lm_b2$coefficients[2]
slope2_b <- lm_b2$coefficients[3]
slope3_b <- lm_b2$coefficients[4]

 # Graph it to check the fit 
b_lm_graph <- ggplot(data, aes(x=Abatement, y=MC_B)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x+I(x^2)+ I(x^3))
b_lm_graph

#############################################

# Sector C looks exponential, so exponential regression

lm_c <- lm(log(MC_C) ~ Abatement, data = data)
summary(lm_c) # explains 83% of the variance
plot(lm_c) # some of these don't look that good
# graph it:
c_lm_graph <- ggplot(data, aes(x=Abatement, y=MC_C)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = log(y)~x)
c_lm_graph

# store the parameters
int_c <- lm_c$coefficients[1]
slope_c <- lm_c$coefficients[2]

# Linear model for C
lm_c<- lm(MC_C ~ Abatement, data = data)
summary(lm_c) # explains 87% of the variance 

#store parameters for linear model
int_line_c<- lm_c$coefficients[1]
slope_line_c<- lm_c$coefficients[2]

# linear model for MC_D
lm_d<- lm(MC_D ~ Abatement, data = data)
summary(lm_d)

#Store parameters
int_line_d<- lm_d$coefficients[1]
slope_line_d<- lm_d$coefficients[2]

################################################
```
graphs of all the sectors

```{r}

# sector A - linear regression
A_lm_graph <- ggplot(data, aes(x=Abatement, y=MC_A)) +
  geom_point() + 
  geom_abline(aes(intercept = int_a, slope = slope_a, col = "red"), show.legend = FALSE) +
  labs(
    y = "Marginal Cost Sector A"
  ) +
  theme_classic()
A_lm_graph

# sector B - polynomial regression
b_graph <- ggplot(data, aes(x=Abatement, y=MC_B)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x+I(x^2)+ I(x^3)) # this isn't right
b_graph

# Sector C
# sos exponential is being complicated
fake_mc <- seq(1, 150, 1)
sectorc <- exp(predict(lm_c, Abatement=fake_mc))
c_graph <- ggplot(data, aes(x=Abatement, y=MC_C)) +
  geom_point() + 
  geom_line(aes(fake_mc, sectorc))
c_graph

# here is the line graph for sector C
c_line_graph <- ggplot(data, aes(x=Abatement, y=MC_C)) +
  geom_point() + 
  geom_abline(aes(intercept = int_line_c, slope = slope_line_c), col = "red") +
  labs(
    y = "Marginal Cost Sector C"
  ) +
  theme_classic()
c_line_graph

# sector D

d_graph <- ggplot(data, aes(x=Abatement, y=MC_D)) +
  geom_point() + 
  geom_abline(aes(intercept = int_line_d, slope = slope_line_d, col = "red"), show.legend = FALSE) +
  labs(
    y = "Marginal Cost Sector D"
  ) +
  theme_classic()
d_graph

```



2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?
```{r}

A<- function(x){int_a + slope_a*(180-x)}
A(1)
# WTP for the first unit 94.61022 

B<- function(x){int_b + slope1_b*(200 -x) + slope2_b*(200 - x)^2 + slope3_b*(200 -x)^3} #let's use this one
B(1)
# WTP for the first unit 6.092104 

B_line<- function(x){int_line_b + slope_line_b*(200-x)}
B_line(1)
# WTP for the first unit with a linear model is  48.86781

C <- function(x){int_c + slope_c*(220 - x)}

C_line<- function(x){int_c + slope_c*(220 - x)}
C_line(1)
# WTP for the first unit 6.666876

D_line<- function(x){int_line_d + slope_line_d*(300 - x)}
D_line(1)
# WTP for the first uit 87.40584


```

Draw demand curves on a graph:
```{r}

demand <- ggplot(data, aes(x=Abatement, y=MC_A)) +
  stat_function(fun = A, col = "red") +
  stat_function(fun = B_line, col = "blue") +
  stat_function(fun = C_line, col = "green") +
  stat_function(fun = D_line, col = "orange") +
  scale_x_continuous(expand = c(0,0)) +
  labs(
    y = "Price ($)",
    x = "Unit Carbon Emissions"
  ) +
  theme_classic()
  
demand

```



3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: 
  (1) the total cost of meeting the target in country X, 
  (2) the cost (or benefit) to each sector, and 
  (3) the tax revenue generated.
  
a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300).
```{r}

# to do this I am juat going to um the MC for seach sector uo until 100 ton isreached this seems too simple let me know what you think

# cost of reducing by 100 ton in sector A
cost_A_100<- sum(data$MC_A[0:11])
# 220.5025

# cost of reducing by 100 ton in sector B
cost_B_100<-sum(data$MC_B[0:11])
# 209.572

# cost of reducing by 100 ton in sector C
cost_C_100<-sum(data$MC_C[0:11])
# 264.1305

# total cost of reducing emissions by 300 ton
total_cost_100<- cost_A_100 + cost_B_100 + cost_C_100
total_cost_100
#694.205

# No tax revenue generated as it is a cap and not a tax??
```


b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

```{r}
# dicide the total cost found above and divide by 300 to get the tax per ton of carbon emitted ??

tax<- total_cost_100/300
tax
#  2.314017 per ton of carbon emitted

# cost to each sector
cost_per_sector_tax<- tax*100
cost_per_sector_tax
# 231.4017

# tax revenue from the tax

tax_rev<- tax*300
tax_rev
# 694.205




```

c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.
```{r}
# first need to aggregate the demand curves horizonatally 

deno = slope_a * slope_line_b + slope_a * slope_line_c + slope_line_b * slope_line_c

agg_y_int = (int_a*slope_line_b*slope_line_c/deno) + (int_line_b*slope_a*slope_line_c/deno) + (int_line_c*slope_line_c*slope_a/deno)

agg_coeff = (slope_a*slope_line_b*slope_line_c/deno)

agg_abate_reverse <- function(x){
  agg_coeff*x + agg_y_int
}
agg_abate_reverse(300)

```

MC lines:

```{r}

# To test how much abatement each place would need at the price of the aggregate MC curve

A_MC <- function(x){(-int_a + x)/slope_a}
A_MC(39.43) # 73.89752 

B_MC<- function(x){(-int_line_b + x)/slope_line_b}

B_MC(39.43) # 124.1042 

C_MC <- function(x){(-int_line_c + x)/slope_line_c}
C_MC(39.43) 

# MC
A_2<- function(x){int_a + slope_a*(x)}

B_2<- function(x){int_line_b + slope_line_b*(x)}

C_2<- function(x){int_line_c + slope_line_c*(x)}

# given the abatement, what is the price?
net_abate = function(x) {
  a = A_2(x)
  b = B_2(x)
  c= C_2(x)
  
  return(a + b + c)
}

net_abate(300)


# given the price, what is the abatement?
net_abate = function(x) {
  a = A_MC(x)
  b = B_MC(x)
  c= C_MC(x)
  
  return(a + b + c)
}

net_abate(39.4)
```


Graph:

```{r}


ggplot(data.frame(x=c(0,200)), aes(x=x)) + 
    stat_function(fun=A, geom ="line", aes(color = "A")) + 
    stat_function(fun=B_line, geom ="line", aes(color = "B")) +
    stat_function(fun=C_line, geom ="line", aes(color = "C")) +
    stat_function(fun=agg_abate_reverse, geom ="line", aes(color = "Aggregated"))+
    labs(x = "Abatement", y = "Price")+
    scale_x_continuous(limits =c(0,300), expand = c(0,0))+
    scale_y_continuous(limits=c(0,50), expand=c(0,0))+
    theme_bw()


MC_ag <- ggplot(data, aes(x=Abatement, y=MC_A)) +
  stat_function(fun = A_MC, col = "red") +
  stat_function(fun = B_MC, col = "blue") +
  stat_function(fun = C_MC, col = "green") +
  stat_function(fun=agg_abate_reverse, geom ="line", aes(color = "Aggregated"))+
  scale_x_continuous(expand = c(0,0), limits = c(0,350)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  labs(
    y = "Price ($)",
    x = "Abatement"
  ) +
  theme_classic()
  
MC_ag


```





4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market?

redo for 4 sectors and find the new amount of abatement for each sector under cap and trade
```{r}
# How much does it cost country Y (sector D) to abate to 300

MC_D<- function(x){int_line_d + slope_line_d*(x)}
MC_D(300) #87.66577 

d_per_unit_carbon <- MC_D(300)/300
d_per_unit_carbon
# So country X would have to pay more than $  0.2922192  per unit ccarbon for country Y to be interested

# oer units abatement costs for A, B, C
C_A<- function(x){int_a + slope_a*(x)}
A_per_unit_carbon <- C_A(300)/300
A_per_unit_carbon # 0.548027 

C_B<- function(x){int_line_b + slope_line_b*(x)}
B_per_unit_carbon <- C_B(300)/300
B_per_unit_carbon #   0.2298033 

C_C<- function(x){int_line_c + slope_line_c*(x)}
C_per_unit_carbon <- C_C(300)/300
C_per_unit_carbon  #0.7449765 



```


5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y.
a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?

```{r}
# just add 1 to each MC function

```


b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?

c. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?

net benefit to firm A
tax: total abatement cost
what they pay in tax
tax*quanitity






